Effectiveness of COVID-19 Booster doses in England: a sequential trials study in OpenSAFELY: Supplementary materials

### 2022-02-22 manuscript/draft-supplement.Rmd

flowchart <- read_csv(fs::path(output_dir_os, "flowchart.csv"))
cohortsummary <- read_csv(fs::path(output_dir_os, "cohortsummary.csv"))
matchsummary <- read_csv(fs::path(output_dir_os, "matchsummary.csv"))
matchsummary_treated <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 1L)
matchsummary_control <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 0L)
matchcoverage <- read_csv(fs::path(output_dir_os, "matchcoverage.csv"))
incidences <- read_csv(fs::path(output_dir_os, "incidence.csv")) %>% mutate(events=events_1+events_0)

@@

hazards_vax12_type <- read_csv(fs::path(output_dir_os, "vax12_type", "effects.csv")) %>%
  mutate(
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level_descr = fct_inorder(subgroup_level_descr),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    #model_name = fct_inorder(str_wrap(model_name, 15)),
    hr_display = paste0(number_format(accuracy=0.01)(hr), " (", number_format(accuracy=0.01)(hr.ll), "-", number_format(accuracy=0.01)(hr.ul), ")")
  )

@@

```{r flowchart, echo=FALSE, warning=FALSE, message=FALSE}
flowchart %>%
  transmute(
    Participants = str_wrap(criteria, 40),
    N = n,
    `N excluded` = n_exclude,
    #`% excluded` = pct_exclude,
    `% remaining` = pct_all
  ) %>%
  # mutate(
  #   Participants=if_else(row_number()==1,"HCWs aged 18-64 receiving BNT162b2 or ChAdOx1 between 4 Jan and 28 Feb",  Participants)
  # ) %>%
  gt() %>%
  fmt_percent(
    columns = starts_with(c("%")),
    decimals = 1
  ) %>%
  fmt_number(
    columns = starts_with(c("N")),
    decimals= 0
  ) %>%
  fmt_missing(
    everything(),
    missing_text="-"
  ) %>%
  tab_style(
    style=cell_text(whitespace ="pre-wrap"),
    #style=cell_text(style ="italic"),
    locations = cells_body(columns = "Participants")
  )
```

>>>>

flowchart <- read_csv(fs::path(output_dir_os, "flowchart.csv"))
cohortsummary <- read_csv(fs::path(output_dir_os, "cohortsummary.csv"))
matchsummary <- read_csv(fs::path(output_dir_os, "matchsummary.csv"))
matchsummary_treated <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 1L)
matchsummary_control <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 0L)
matchcoverage <- read_csv(fs::path(output_dir_os, "matchcoverage.csv"))
matchflowchart <- read_csv(fs::path(output_dir_os, "matchflowchart.csv"))
incidences <- read_csv(fs::path(output_dir_os, "incidence.csv")) %>% mutate(events=events_1+events_0)

@@

hazards_vax12_type <- read_csv(fs::path(output_dir_os, "vax12_type", "effects.csv")) %>%
  mutate(
    model_descr = fct_inorder(model_descr),
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level_descr = fct_inorder(subgroup_level_descr),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    #model_name = fct_inorder(str_wrap(model_name, 15)),
    hr_display = paste0(number_format(accuracy=0.01)(hr), " (", number_format(accuracy=0.01)(hr.ll), "-", number_format(accuracy=0.01)(hr.ul), ")")
  )

@@

```{r flowchart, echo=FALSE, warning=FALSE, message=FALSE}

matchflowchart %>%
  transmute(
    treatment,
    stage,
    criteria = str_wrap(criteria, 40),
    n,
    n_exclude,
    pct_all
  ) %>%
  pivot_wider(
    id_cols = c(stage, criteria),
    names_from = treatment,
    values_from = c(n, n_exclude, pct_all)
  ) %>%
  gt() %>%
  cols_label(
    stage="",
    criteria = "",

    n_pfizer = "N",
    #n_moderna = "N",

    n_exclude_pfizer = "N excluded",
    #n_exclude_moderna = "N excluded",

    pct_all_pfizer = "% remaining",
    #pct_all_moderna = "% remaining",
  ) %>%
  tab_spanner(
    label = "BNT162b2",
    columns = ends_with("pfizer")
  ) %>%
  # tab_spanner(
  #   label = "mRNA-1273",
  #   columns = ends_with("moderna")
  # ) %>%
  fmt_percent(
    columns = starts_with(c("pct_")),
    decimals = 1
  ) %>%
  fmt_number(
    columns = starts_with(c("n_")),
    decimals= 0
  ) %>%
  fmt_missing(
    everything(),
    missing_text="-"
  ) %>%
  tab_style(
    style=cell_text(whitespace ="pre-wrap"),
    #style=cell_text(style ="italic"),
    locations = cells_body(columns = "criteria")
  )
```
